Short Paper

### 2023-03-10 Thesis/MethodX/Manuscript/Manuscript.Rmd
manuskrip

---
title: Optimization model for multi-product multi-period multi-supplier raw-material selection and composition, and order quantity problem with minimum one-year order quantity contract
author:
  - name: Mohammad Rizka Fadhli
    email: 20921004@mahasiswa.itb.ac.id
    correspondingauthor: true
    affiliation: lala
  - name: Saladin Uttunggadewa
    affiliation: lili
  - name: Rieske Hadianti
    affiliation: lulu
  - name: Sri Redjeki Pudjaprasetya
    affiliation: lili
address:
  - code: lala
    address: Magister of Computational Sciences Program, Faculty of Mathematics and Natural Sciences, Institut Teknologi Bandung
  - code: lili
    address: Faculty of Mathematics and Natural Sciences, Institut Teknologi Bandung
  - code: lulu
    address: Center for Mathematical Modeling and Simulation, Institut Teknologi Bandung
abstract: |
  This paper concerns the optimization model for a multi-product multi-period raw-material selection and composition, and order quantity problem faced by a beverage company. There are some criteria in raw material selection, which we accommodate all the criteria in the objective function. There are a number of suppliers, and one of the decision criteria is minimum one-year order quantity contract between the company and the suppliers. The actual one-year demand of raw materials may deviate significantly from the minimum one-year order quantities. In this paper, we derive a function that can be regarded as a penalty function in order to maintain the total order quantities in one year fulfil the minimum one-year order quantity contracts. This penalty function is  a part of the objective function and can be relaxed once the minimum one-year order quantity contracts are fulfilled.

@@

while minimizing the total inventory cost.

@@

$$
\begin{matrix}
minimize & F(\bar{x},\bar{z}) \\
subject \space to & Constraint \space I-VIII \\
 & x_k, \hat{x}_{jk}, z_{jk} \in \mathbb{Z}^+, y_k, a_{ijk} \in \left\{0,1 \right\}, 0 \leq b_{ijk} \leq 1
\end{matrix}
$$

>>>>

---
title: Optimization model for multi-product multi-period multi-supplier raw-material selection and composition, and order quantity problem with minimum one-year order quantity contract
author:
  - name: Mohammad Rizka Fadhli
    email: 20921004@mahasiswa.itb.ac.id
    correspondingauthor: true
    affiliation: a1
  - name: Saladin Uttunggadewa
    email: s_uttunggadewa@math.itb.ac.id
    affiliation: a2
  - name: Rieske Hadianti
    email: ike.hadianti@gmail.com
    affiliation: a3
  - name: Sri Redjeki Pudjaprasetya
    email: srpudjap@gmail.com
    affiliation: a2
address:
  - code: a1
    address: Master's Program in Computational Science; Faculty of Mathematics and Natural Sciences; Institut Teknologi Bandung
  - code: a2
    address: Faculty of Mathematics and Natural Sciences; Institut Teknologi Bandung
  - code: a3
    address: Center for Mathematical Modeling and Simulation; Institut Teknologi Bandung
abstract: |
  This paper concerns the optimization model for a multi-product multi-period raw-material selection and composition, and order quantity problem faced by a beverage company. There are some criteria in raw material selection, which we accommodate all the criteria in the objective function. There are a number of suppliers, and one of the decision criteria is minimum one-year order quantity contract between the company and the suppliers. The actual one-year demand of raw materials may deviate significantly from the minimum one-year order quantities. In this paper, we derive a function that can be regarded as a penalty function in order to maintain the total order quantities in one year fulfil the minimum one-year order quantity contracts. This penalty function is  a part of the objective function and can be relaxed once the minimum one-year order quantity contracts are fulfilled.

@@

\setlength{\parindent}{0pt} while minimizing the total inventory cost.

\setlength{\parindent}{10pt}

@@

$$
\begin{matrix}
\text{minimize} & F(\bar{x},\bar{z}) \\
\text{subject to} & \text{Constraint I-VIII} \\
 & x_k, \hat{x}_{jk}, z_{jk} \in \mathbb{Z}^+, y_k, a_{ijk} \in \left\{0,1 \right\}, 0 \leq b_{ijk} \leq 1
\end{matrix}
$$

### 2023-03-10 Thesis/MethodX/Manuscript/Manuscript.tex
manuskrip

  \title{Optimization model for multi-product multi-period
multi-supplier raw-material selection and composition, and order
quantity problem with minimum one-year order quantity contract}
    \author[lala]{Mohammad Rizka Fadhli%
  \corref{cor1}%
  }
   \ead{20921004@mahasiswa.itb.ac.id} 
    \author[lili]{Saladin Uttunggadewa%
  %
  }

    \author[lulu]{Rieske Hadianti%
  %
  }

    \author[lili]{Sri Redjeki Pudjaprasetya%
  %
  }

      \affiliation[lala]{Magister of Computational Sciences Program,
Faculty of Mathematics and Natural Sciences, Institut Teknologi Bandung}
    \affiliation[lili]{Faculty of Mathematics and Natural Sciences,
Institut Teknologi Bandung}
    \affiliation[lulu]{Center for Mathematical Modeling and Simulation,
Institut Teknologi Bandung}
    \cortext[cor1]{Corresponding author}

@@

\[
\begin{matrix}
minimize & F(\bar{x},\bar{z}) \\
subject \space to & Constraint \space I-VIII \\
 & x_k, \hat{x}_{jk}, z_{jk} \in \mathbb{Z}^+, y_k, a_{ijk} \in \left\{0,1 \right\}, 0 \leq b_{ijk} \leq 1
\end{matrix}
\]

>>>>

  \title{Optimization model for multi-product multi-period
multi-supplier raw-material selection and composition, and order
quantity problem with minimum one-year order quantity contract}
    \author[a1]{Mohammad Rizka Fadhli%
  \corref{cor1}%
  }
   \ead{20921004@mahasiswa.itb.ac.id} 
    \author[a2]{Saladin Uttunggadewa%
  %
  }
   \ead{s\_uttunggadewa@math.itb.ac.id} 
    \author[a3]{Rieske Hadianti%
  %
  }
   \ead{ike.hadianti@gmail.com} 
    \author[a2]{Sri Redjeki Pudjaprasetya%
  %
  }
   \ead{srpudjap@gmail.com} 
      \affiliation[a1]{Master's Program in Computational Science;
Faculty of Mathematics and Natural Sciences; Institut Teknologi Bandung}
    \affiliation[a2]{Faculty of Mathematics and Natural Sciences;
Institut Teknologi Bandung}
    \affiliation[a3]{Center for Mathematical Modeling and Simulation;
Institut Teknologi Bandung}
    \cortext[cor1]{Corresponding author}

@@

\[
\begin{matrix}
\text{minimize} & F(\bar{x},\bar{z}) \\
\text{subject to} & \text{Constraint I-VIII} \\
 & x_k, \hat{x}_{jk}, z_{jk} \in \mathbb{Z}^+, y_k, a_{ijk} \in \left\{0,1 \right\}, 0 \leq b_{ijk} \leq 1
\end{matrix}
\]

### 2023-03-10 Thesis/MethodX/Untitled/Untitled.Rmd
manuskrip

---
title: An R-based end-to-end optimization program for multi-product multi-period multi-supplier raw-material selection and composition, and order quantity problem with minimum one-year order quantity contract
author:
  - name: Mohammad Rizka Fadhli
    email: 20921004@mahasiswa.itb.ac.id
    correspondingauthor: true
    affiliation: lala
  - name: Saladin Uttunggadewa
    affiliation: lili
  - name: Rieske Hadianti
    affiliation: lulu
  - name: Sri Redjeki Pudjaprasetya
    affiliation: lili
address:
  - code: lala
    address: Magister of Computational Sciences Program, Faculty of Mathematics and Natural Sciences, Institut Teknologi Bandung
  - code: lili
    address: Faculty of Mathematics and Natural Sciences, Institut Teknologi Bandung
  - code: lulu
    address: Center for Mathematical Modeling and Simulation, Institut Teknologi Bandung
abstract: |
  This paper concerns the optimization model for a multi product multi period raw-material selection and composition, and order quantity problem faced by a beverage company. There are some criteria in raw material selection, which we accommodate all the criteria in the objective function. There are a number of suppliers, and one of the decision criteria is minimum one-year order quantity contracts between the company and the suppliers. The actual one-year demand of raw materials may deviate significantly from the minimum one-year order quantities. In this paper, we derive a function that can be regarded as a penalty function in order to maintain the total order quantities in one year fulfill the minimum one-year order quantity contracts. This penalty function is  a part of the objective function, and can be relaxed once the the minimum one-year order quantity contracts are fulfilled. 
  This optimization problem defined as mixed integer linear programming. We create an R-based end-to-end program to solve this optimization problem. Using various data inputs such as raw-material details, product's raw-material composition, and products demand, the end results of the program is weekly raw-material order allocation and composition. This program can be used in various manufacture industry.
keywords: 
  - inventory control
  - multi criteria raw-material selection
  - mix-integer linear programming
  - R programming
journal: "Software X"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: mybibfile.bib
linenumbers: false
numbersections: true
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
---

# Introduction

This paper concerns the optimization model for supplier selection, order allocation, and raw-material composition in a beverage company that produces a large number of drink powders. There are a number of suppliers that can provide the same key raw material of the drink powders, but the color or some physical characteristics are slightly different so we may assume those raw materials are different. The drink powders produced by this company, which in the remainder of this paper are called items, can be classified into two classes of items.

  - The first class consists of items that can be produced by using exactly a single type of raw material.
  - The second class consists of more flexible items, where each item in this class can be produced by using one raw material or by using a composition of a number of raw materials. For each item in this class, we then have a set of possible raw materials. The sets of possible materials may vary from one to the other.

In order to avoid supply disruption, the company decides to use multiple sources for these raw materials. The company has established selection criteria for each raw material, which are based on the estimated one-year total demand of raw materials and  a subjective assessment of whether the raw material cannot be substituted, price, service, and the minimum order required for each purchase. After determining the score for each raw material, the company decided to make contracts or agreements with six suppliers. Each contract stated the unit price price and the minimum order quantity within a year. Based on these contracts, production planning and inventory control of raw materials are carried out.

The estimated total one-year demand for items is obtained from the forecasting process performed yearly.  This forecasting process yields the monthly total demand for items, which is time varying. But at the production level, the company refines the monthly total demand on a monthly basis as a response to some disruptions such as sudden additional requests due to flash sales practices in e-commerce, and others.

Once the demand for items for a month is issued, the company must perform the decision for purchasing the raw materials from some suppliers. This purchase decision from a supplier includes purchase for four serial deliveries one week apart. The first delivery must be no later than 17 days before the following  month's start. The period of 17 days here is the total time required for  the company's internal inspection and preparation of raw materials.

This decision process is a complex one since there are a large number of items that have to be produced which mostly belong to the second class, and the monthly demand may vary. Additionally, the company imposes a production regulation for the second class of items as a result of the multiple-sources policy, which states that each item in the second class must be produced using a composition of at least two types of the corresponding possible raw materials. The decision process must be performed carefully in order to obtain results in the form of:

  - which raw materials are purchased along with the delivery size for every four corresponding weeks, 
  - the composition of raw materials for every item in the second class which has to be produced,

while minimizing the total inventory cost.

The company developed a decision support system for this monthly decision process, which is developed based on an optimization model.

\newpage

# Hapus

@@

Here are two sample references: @Feynman1963118.

uji coba [@Dirac1953888]

>>>>

---
title: Short Paper
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliation: Some Institute of Technology
    correspondingauthor: true
    footnote: 1
  - name: Bob Security
    email: bob@example.com
    affiliation: Another University
  - name: Cat Memes
    email: cat@example.com
    affiliation: Another University
    footnote: 2
  - name: Derek Zoolander
    email: derek@example.com
    affiliation: Some Institute of Technology
    footnote: 2
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "This is the first author footnote."
  - code: 2
    text: "Another author footnote."
abstract: |
  This is the abstract.

  It consists of two paragraphs.
keywords: 
  - keyword1
  - keyword2
journal: "An awesome journal"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: mybibfile.bib
linenumbers: false
numbersections: true
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
---

@@

Here are two sample references: @Feynman1963118 [@Dirac1953888].

### 2023-03-10 Thesis/MethodX/Untitled/Untitled.tex
manuskrip

  \journal{Software X} % Sets Journal name

@@

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={An R-based end-to-end optimization program for multi-product multi-period multi-supplier raw-material selection and composition, and order quantity problem with minimum one-year order quantity contract},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

@@

  \title{An R-based end-to-end optimization program for multi-product
multi-period multi-supplier raw-material selection and composition, and
order quantity problem with minimum one-year order quantity contract}
    \author[lala]{Mohammad Rizka Fadhli%
  \corref{cor1}%
  }
   \ead{20921004@mahasiswa.itb.ac.id} 
    \author[lili]{Saladin Uttunggadewa%
  %
  }

    \author[lulu]{Rieske Hadianti%
  %
  }

    \author[lili]{Sri Redjeki Pudjaprasetya%
  %
  }

      \affiliation[lala]{Magister of Computational Sciences Program,
Faculty of Mathematics and Natural Sciences, Institut Teknologi Bandung}
    \affiliation[lili]{Faculty of Mathematics and Natural Sciences,
Institut Teknologi Bandung}
    \affiliation[lulu]{Center for Mathematical Modeling and Simulation,
Institut Teknologi Bandung}
    \cortext[cor1]{Corresponding author}

  \begin{abstract}
  This paper concerns the optimization model for a multi product multi
  period raw-material selection and composition, and order quantity
  problem faced by a beverage company. There are some criteria in raw
  material selection, which we accommodate all the criteria in the
  objective function. There are a number of suppliers, and one of the
  decision criteria is minimum one-year order quantity contracts between
  the company and the suppliers. The actual one-year demand of raw
  materials may deviate significantly from the minimum one-year order
  quantities. In this paper, we derive a function that can be regarded
  as a penalty function in order to maintain the total order quantities
  in one year fulfill the minimum one-year order quantity contracts.
  This penalty function is a part of the objective function, and can be
  relaxed once the the minimum one-year order quantity contracts are
  fulfilled. This optimization problem defined as mixed integer linear
  programming. We create an R-based end-to-end program to solve this
  optimization problem. Using various data inputs such as raw-material
  details, product's raw-material composition, and products demand, the
  end results of the program is weekly raw-material order allocation and
  composition. This program can be used in various manufacture industry.
  \end{abstract}
    \begin{keyword}
    inventory control \sep multi criteria raw-material
selection \sep mix-integer linear programming \sep 
    R programming
  \end{keyword}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

This paper concerns the optimization model for supplier selection, order
allocation, and raw-material composition in a beverage company that
produces a large number of drink powders. There are a number of
suppliers that can provide the same key raw material of the drink
powders, but the color or some physical characteristics are slightly
different so we may assume those raw materials are different. The drink
powders produced by this company, which in the remainder of this paper
are called items, can be classified into two classes of items.

\begin{itemize}
\tightlist
\item
  The first class consists of items that can be produced by using
  exactly a single type of raw material.
\item
  The second class consists of more flexible items, where each item in
  this class can be produced by using one raw material or by using a
  composition of a number of raw materials. For each item in this class,
  we then have a set of possible raw materials. The sets of possible
  materials may vary from one to the other.
\end{itemize}

In order to avoid supply disruption, the company decides to use multiple
sources for these raw materials. The company has established selection
criteria for each raw material, which are based on the estimated
one-year total demand of raw materials and a subjective assessment of
whether the raw material cannot be substituted, price, service, and the
minimum order required for each purchase. After determining the score
for each raw material, the company decided to make contracts or
agreements with six suppliers. Each contract stated the unit price price
and the minimum order quantity within a year. Based on these contracts,
production planning and inventory control of raw materials are carried
out.

The estimated total one-year demand for items is obtained from the
forecasting process performed yearly. This forecasting process yields
the monthly total demand for items, which is time varying. But at the
production level, the company refines the monthly total demand on a
monthly basis as a response to some disruptions such as sudden
additional requests due to flash sales practices in e-commerce, and
others.

Once the demand for items for a month is issued, the company must
perform the decision for purchasing the raw materials from some
suppliers. This purchase decision from a supplier includes purchase for
four serial deliveries one week apart. The first delivery must be no
later than 17 days before the following month's start. The period of 17
days here is the total time required for the company's internal
inspection and preparation of raw materials.

This decision process is a complex one since there are a large number of
items that have to be produced which mostly belong to the second class,
and the monthly demand may vary. Additionally, the company imposes a
production regulation for the second class of items as a result of the
multiple-sources policy, which states that each item in the second class
must be produced using a composition of at least two types of the
corresponding possible raw materials. The decision process must be
performed carefully in order to obtain results in the form of:

\begin{itemize}
\tightlist
\item
  which raw materials are purchased along with the delivery size for
  every four corresponding weeks,
\item
  the composition of raw materials for every item in the second class
  which has to be produced,
\end{itemize}

while minimizing the total inventory cost.

The company developed a decision support system for this monthly
decision process, which is developed based on an optimization model.

\newpage

\hypertarget{hapus}{%
\section{Hapus}\label{hapus}}

@@

Here are two sample references: \citet{Feynman1963118}.

uji coba \citep{Dirac1953888}

@@

{\centering \includegraphics[width=0.5\linewidth]{Manuscript_files/figure-latex/fig2-1}

>>>>

  \journal{An awesome journal} % Sets Journal name

@@

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Short Paper},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

@@

  \title{Short Paper}
    \author[Some Institute of Technology]{Alice Anonymous%
  \corref{cor1}%
  \fnref{1}}
   \ead{alice@example.com} 
    \author[Another University]{Bob Security%
  %
  }
   \ead{bob@example.com} 
    \author[Another University]{Cat Memes%
  %
  \fnref{2}}
   \ead{cat@example.com} 
    \author[Some Institute of Technology]{Derek Zoolander%
  %
  \fnref{2}}
   \ead{derek@example.com} 
      \affiliation[Some Institute of Technology]{Department, Street,
City, State, Zip}
    \affiliation[Another University]{Department, Street, City, State,
Zip}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

  \begin{abstract}
  This is the abstract.

  It consists of two paragraphs.
  \end{abstract}
    \begin{keyword}
    keyword1 \sep 
    keyword2
  \end{keyword}

@@

@@

Here are two sample references: \citeauthor{Feynman1963118}
\citetext{\citeyear{Feynman1963118}; \citealp{Dirac1953888}}.

@@

{\centering \includegraphics[width=0.5\linewidth]{Untitled_files/figure-latex/fig2-1}
